\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-12 ext-ind-type-compilation-example.tex
Small Fixes.

\begin{lstlisting}
(* Type Checking of Inductive Type *) [@\tanc{Tyck-IndTy-start}@]
Module Type STLC_Ctx1. 
(* The Context including Inductive Type *)
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Ctx1.
Module Type tm_prec_64 (self: tm_6). 
Parameter (* Type for partial recursor *)
(tm_prec : ∀ t, ∀ P : self.tm -> Type,
  (∀ n, option (P (self.tm_var n))) -> 
  [@\dadada@], option (P t)).
End tm_prec_64.
Module Type STLC_Ctx2.  
  Include STLC_Ctx1.
  Include tm_prec_64. (* New Ctx include prec *)
End STLC_Ctx2.
(* [@\dadada@] etc, everytime a new field is added, a new 
module type is created as the ctx with the new field *)
(* Collect eliminator TYPE for later type-check *)
Module tm_rec_type (self: STLC_Ctx1).
  Definition _TYPE_tm_rec :=
    ∀ P : self.tm -> Set,
    ( ∀ n, P (self.tm_var n)) ->
    ( ∀ n i, P i -> P (self.tm_abs n i)) ->
    [@\dadada@] -> ∀ i : self.tm, P i.
End tm_rec_type.  [@\tanc{Tyck-IndTy-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
(* Compilation, only when closing a top-level family *) [@\tanc{Cmp-Result-start}@]
(* Ctx that expose concrete inductive type *)
Module Type STLC_CCtx1.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End STLC_CCtx.
(* The compilation of recursor and[@\dadada@] *)
Module subst_128 (self: STLC_CCtx1).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* [@\dadada@] the compilation of partial recursor, 
both require concrete inductive type in the ctx *)
Module tm_prec_72 (self: STLC_CCtx1).
Definition tm_prec :
  ∀ t, ∀ P : self.tm -> Type,
  (∀ n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P t) := [@\dadada@]
End tm_prec_72. 
Module STLC. (* Assembling/Compiling the whole STLC *)
Include tm_5. Include tm_prec_72. 
Include tm_prectm_81. (* Justification for comp axiom *)
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
Module subst_internal_248 (STLC_bool: STLC_Ctx1).
Include tm_true_197 STLC_bool. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle STLC_bool. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion Compilation *)
Module subst_242 (self: [@\dadada@]).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@]
    self.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}

>>>>

\begin{lstlisting}
(* Type Checking of Inductive Type *) [@\tanc{Tyck-IndTy-start}@]
(* Tyck happens during interactively creating families*)
Module Type STLC_Ctx1. 
(* The Context including Inductive Type *)
  Parameter (tm : Set).
  Parameter (tm_var : id → tm).
  Parameter (tm_abs : id → tm → tm).
  (* [@\dadada@] and all the fields for inductive type [@\dadada@] *)
End STLC_Ctx1.
Module Type tm_prec_64 (self: tm_6). 
Parameter (* Type for partial recursor *)
(tm_prec : ∀ t, ∀ P : self.tm -> Type,
  (∀ n, option (P (self.tm_var n))) -> 
  [@\dadada@], option (P t)).
End tm_prec_64.
Module Type STLC_Ctx2.  
  Include STLC_Ctx1.
  Include tm_prec_64. (* New Ctx include prec *)
End STLC_Ctx2.
(* [@\dadada@] etc, everytime a new field is added, a new 
module type is created as the ctx with the new field *)
(* Collect eliminator TYPE for later type-check *)
Module tm_rec_type (self: STLC_Ctx1).
  Definition _TYPE_tm_rec :=
    ∀ P : self.tm -> Set,
    ( ∀ n, P (self.tm_var n)) ->
    ( ∀ n i, P i -> P (self.tm_abs n i)) ->
    [@\dadada@] -> ∀ i : self.tm, P i.
End tm_rec_type.  [@\tanc{Tyck-IndTy-end}@]
\end{lstlisting}

@@

\begin{lstlisting}
(* Compilation, happens when closing a top-level family *) [@\tanc{Cmp-Result-start}@]
(* Ctx that expose concrete inductive type *)
Module Type STLC_CCtx.
Inductive __internal_tm : Set := [@\dadada@] 
Include subst_internal_410. (* [@\dadada@] and more inclusion *)
End STLC_CCtx.
(* Both the compilation of recursor and[@\dadada@] *)
Module subst_128 (self: STLC_CCtx).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@] .
End subst_128.
(* [@\dadada@]the compilation of partial recursor 
require concrete inductive type exposed in the ctx *)
Module tm_prec_72 (self: STLC_CCtx[@\dadada@]).
Definition tm_prec :
  ∀ t, ∀ P : self.tm -> Type,
  (∀ n, option (P (self.tm_var n))) ->
  [@\dadada@], option (P t) := [@\dadada@]
End tm_prec_72. 
Module STLC. (* Assembling/Compiling the whole STLC *)
Include tm_5. Include tm_prec_72. 
Include tm_prectm_81. (*Justify comp axiom, mostly eq_refl*)
Include subst_internal_410. Include subst_128.
End v_129.
(* Assembling STLC_bool.subst_internal via reusing 
    most of the former compilation results *)
(* Notice how handlers don't require explicitly
   exposing the inductive type *)
Module subst_internal_248 (self: STLC_Ctx1).
(* The New Handlers *)
Include tm_true_197 self. Include [@\dadada@]
(* The Reused Compilation result *)
Include tm_var_handle self. Include [@\dadada@]
End v_248. 
(* Regenerated FRecursion Compilation *)
Module subst_242 (self: [@\dadada@]).
Include __motive_of_subst_107 self.
Definition subst :=
  self.__internal_tm_rec __motiveTsubst
	self.subst_internal.tm_var [@\dadada@]
    self.subst_internal.tm_true [@\dadada@] .
End subst_242. [@\tanc{Cmp-Result-end}@]
\end{lstlisting}
